### 2018-07-26 express2018/formal.tex
Fixed bibitem of LCF

Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic}, which traces
its roots back to
\emph{Edinburgh LCF} by Robin Milner and others in 1972, is a variant of
Church’s simple theory of types (STT) \cite{church1940formulation},
plus a higher order version of Hilbert's choice operator $\varepsilon$,
Axiom of Infinity, and Rank-1 (prenex) polymorphism.
HOL4 has implemented the original HOL Logic, 
while some other theorem provers in HOL family (e.g. Isabelle/HOL) have
certain extensions.
%  (they made the formal language more powerful,
% but they also bring the possibilities that the entire logic becomes
% inconsistent). 
Indeed the HOL Logic has considerable simpler logical
foundations than most other theorem provers. %, e.g. Coq. 
As a consequence,
formal theories built in HOL is easily convincible and can
also be easily ported to other proof systems,
sometimes automatically \cite{hurd2011opentheory}.

>>>>

Higher Order Logic (or \emph{HOL Logic}) \cite{hollogic}, which traces
its roots back to LCF
\cite{gordon1979edinburgh,milner1972logic} by Robin Milner and others since 1972, is a variant of
Church’s simple theory of types (STT) \cite{church1940formulation},
plus a higher order version of Hilbert's choice operator $\varepsilon$,
Axiom of Infinity, and Rank-1 (prenex) polymorphism.
HOL4 has implemented the original HOL Logic, 
while some other theorem provers in HOL family (e.g. Isabelle/HOL) have
certain extensions.
%  (they made the formal language more powerful,
% but they also bring the possibilities that the entire logic becomes
% inconsistent). 
Indeed the HOL Logic has considerable simpler logical
foundations than most other theorem provers. %, e.g. Coq. 
As a consequence,
formal theories built in HOL is easily convincible and can
also be easily ported to other proof systems,
sometimes automatically \cite{hurd2011opentheory}.
